An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-11-30 latex-spie/article.tex
Benchmark datasets are added

\documentclass[]{spie}  % use for US letter paper
\usepackage{comment}
%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
\usepackage[]{graphicx}
\usepackage{epsfig}		% TeX will automatically convert eps --> pdf in pdflatex	
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabularx}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{bbm}
\usepackage[mathcal]{euscript}
\usepackage{mathtools}

\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

@@

\author{
Can Erhan\supit{a}, 
Evangelos Sariyanidi\supit{b}, 
Onur Sencan\supit{c}, 
Hakan Temeltas\supit{c}
\skiplinehalf
\supit{a}Istanbul Technical University Mechatronics Engineering Department, Maslak 34469, Istanbul, Turkey; 
\supit{b}Queen Mary University of London School of Electronic Engineering and Computer Science, ADDRESS, London, England; 
\supit{c}Istanbul Technical University Control and Automation Engineering Department, Maslak 34469, Istanbul, Turkey
}

@@

\begin{equation}
\mathbf{I}_{p\times q} = \begin{bmatrix}
 I_{11} & \hdots & I_{1Q} \\
 \vdots & \ddots & \vdots \\
 I_{P1} & \hdots & I_{PQ} 
 \end{bmatrix}
 \longrightarrow
 \begin{bmatrix}
 I_{11} \\
 \vdots \\
 I_{1Q} \\
 \vdots \\
 I_{P1} \\
 \vdots \\
 I_{PQ}
 \end{bmatrix}
 \label{eq:divided_mat}
\end{equation}
where $P=\floor*{^p/_k}$ and $Q=\floor*{^q/_k}$. An exemplar input image partitioned into subimages is shown in Figure \ref{fig:divided_image}. The $Z_{nm}$ of the input image can be considered as the transformation of the subimages in (\ref{eq:divided_mat}) individually. This transform is applied to subimages with all $n$ and $m$ values according to its order. Lastly, the transformed subimages contains a set of complex coefficients are collected into a new matrix such as:

\begin{equation}
\mathbf{Z} ( \mathbf{I}_{p\times q} )= 
\begin{bmatrix}
\mathbf{Z}(I_{11}) \\
  \vdots \\
\mathbf{Z}(I_{1Q}) \\
  \vdots \\
\mathbf{Z}(I_{P1}) \\
  \vdots \\
\mathbf{Z}(I_{PQ}) \\
 \end{bmatrix} = 
 \begin{bmatrix}
Z_{00}(I_{11}) & \hdots & Z_{nm}(I_{11}) \\
  \vdots  & & \vdots \\
Z_{00}(I_{1Q}) & \hdots & Z_{nm}(I_{1Q}) \\
  \vdots  & & \vdots \\
Z_{00}(I_{P1}) & \hdots & Z_{nm}(I_{P1}) \\
  \vdots  & & \vdots \\
Z_{00}(I_{PQ}) & \hdots & Z_{nm}(I_{PQ}) \\
 \end{bmatrix} = 
 \begin{bmatrix}
a_{00}^{11} + \mathbf{i}b_{00}^{11} & \hdots & a_{nm}^{11} + \mathbf{i}b_{nm}^{11} \\
  \vdots  & & \vdots \\
a_{00}^{1Q} + \mathbf{i}b_{00}^{1Q} & \hdots & a_{nm}^{1Q} + \mathbf{i}b_{nm}^{1Q} \\
  \vdots  & & \vdots \\
a_{00}^{P1} + \mathbf{i}b_{00}^{P1} & \hdots & a_{nm}^{P1} + \mathbf{i}b_{nm}^{P1} \\
  \vdots  & & \vdots \\
a_{00}^{PQ} + \mathbf{i}b_{00}^{PQ} & \hdots & a_{nm}^{PQ} + \mathbf{i}b_{nm}^{PQ} \\
 \end{bmatrix}.
 \label{eq:lzm_op}
\end{equation}

@@

Images are collected via Kinect mounted moving platform and approximately pointed in the direction of the displacement with average speed $0.25m/s$. Also, the rectangle-shaped trajectory of the three datasets is nearly the same as the others to compare their performances. There are two loops that contains 1000 frames per loop for each dataset, one for discovering, the other for evaluating.

manually annotated, each frame is considered as a different location, similar frame sensitivity is approx 10 frame.

%%% DATASET EXAMPLES
\begin{figure}[!htb]
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=7cm]{figures/dataset_examples.png}
        \caption{Dataset examples: (right) bright, (middle) dim, (left) dark}
        \label{fig:dataset}
\end{figure}

>>>>

\documentclass[]{spie}  % use for US letter paper
\usepackage{comment}
%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
\usepackage[]{graphicx}
\usepackage{epsfig}		% TeX will automatically convert eps --> pdf in pdflatex	
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabularx}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{bbm}
\usepackage[mathcal]{euscript}
\usepackage{mathtools}

\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
%\renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
%\addtolength{\voffset}{9mm}   %>>> moves text field down

@@

\author{
Can Erhan\supit{a}, 
Evangelos Sariyanidi\supit{b}, 
Onur Sencan\supit{c}, 
Hakan Temeltas\supit{c}
\skiplinehalf
\supit{a}Istanbul Technical University Mechatronics Engineering Department, Maslak 34469, Istanbul, Turkey; 
\supit{b}Centre of Intelligent Sensing, Mile End Road, E1 4NS, London, U.K.;
\supit{c}Istanbul Technical University Control and Automation Engineering Department, Maslak 34469, Istanbul, Turkey
}

@@

\begin{equation}
\mathbf{I}_{p\times q} = \begin{bmatrix}
 I_{11} & \hdots & I_{1Q} \\
 \vdots & \ddots & \vdots \\
 I_{P1} & \hdots & I_{PQ} 
 \end{bmatrix}
 \longrightarrow
 \begin{bmatrix}
 I_{11} \\
 \vdots \\
 I_{1Q} \\
 \vdots \\
 I_{P1} \\
 \vdots \\
 I_{PQ}
 \end{bmatrix}
 \label{eq:divided_mat}
\end{equation}
where $P=\floor*{^p/_k}$ and $Q=\floor*{^q/_k}$. An exemplar input image partitioned into subimages is shown in Figure \ref{fig:divided_image}. The $Z_{nm}$ of the input image can be considered as the transformation of the subimages in (\ref{eq:divided_mat}) individually. This transform is applied to subimages with all $n$ and $m$ values according to its order. Lastly, the ZMs computed from transformed subimages are collected into a new matrix as follows:

\begin{equation}
\mathbf{Z} ( \mathbf{I}_{p\times q} )= 
\begin{bmatrix}
\mathbf{Z}(I_{11}) \\
  \vdots \\
\mathbf{Z}(I_{1Q}) \\
  \vdots \\
\mathbf{Z}(I_{P1}) \\
  \vdots \\
\mathbf{Z}(I_{PQ}) \\
 \end{bmatrix}
 \longrightarrow
 \begin{bmatrix}
Z_{00}(I_{11}) & \hdots & Z_{nm}(I_{11}) \\
  \vdots  & & \vdots \\
Z_{00}(I_{1Q}) & \hdots & Z_{nm}(I_{1Q}) \\
  \vdots  & & \vdots \\
Z_{00}(I_{P1}) & \hdots & Z_{nm}(I_{P1}) \\
  \vdots  & & \vdots \\
Z_{00}(I_{PQ}) & \hdots & Z_{nm}(I_{PQ}) \\
 \end{bmatrix} = 
 \begin{bmatrix}
a_{00}^{11} + \mathbf{i}b_{00}^{11} & \hdots & a_{nm}^{11} + \mathbf{i}b_{nm}^{11} \\
  \vdots  & & \vdots \\
a_{00}^{1Q} + \mathbf{i}b_{00}^{1Q} & \hdots & a_{nm}^{1Q} + \mathbf{i}b_{nm}^{1Q} \\
  \vdots  & & \vdots \\
a_{00}^{P1} + \mathbf{i}b_{00}^{P1} & \hdots & a_{nm}^{P1} + \mathbf{i}b_{nm}^{P1} \\
  \vdots  & & \vdots \\
a_{00}^{PQ} + \mathbf{i}b_{00}^{PQ} & \hdots & a_{nm}^{PQ} + \mathbf{i}b_{nm}^{PQ} \\
 \end{bmatrix}.
 \label{eq:lzm_op}
\end{equation}

@@

The images in the datasets are acquired via Kinect mounted moving platform and pointed in the direction of the displacement with average speed $0.25$ m/s. Also, the rectangle-shaped trajectory of the three datasets is nearly the same as the others to compare their performances correctly. There are two loops that contains 1000 frames per loop in each dataset, one is used for discovering and the other one for evaluating. To create the ground truth, the locations which corresponds to approximately 10 sequential frames is annotated manually.

%%% DATASET EXAMPLES
\begin{figure}[!htb]
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, height=7cm]{figures/dataset_examples.png}
        \vspace{2mm}
        \caption{Examplary images belong to benchmark datasets in different lighting conditions which are bright (left), dim (middle) and dark (right).}
        \label{fig:dataset}
\end{figure}
